---
title: "1911_Inter_Data"
author: "Paige Kemp & Chris Wahlheim"
Date: "12/14/2020"
output: html_document
---


# Clear Environment and load packages
```{r clear environment and load packages}
## clear Environment
rm(list=ls())

## load packages
library(tidyverse)
library(magrittr)
library(lme4)
library(car)
library(emmeans)
library(knitr)
library(Hmisc)
```


# Read in Interpolated Data
```{r read in interpolated data}
## read data
Inter_Data <- read.csv("1911_Interpolated_data.csv", stringsAsFactors = FALSE, fileEncoding = "UTF-8-BOM")

## exclude subjects
Inter_Data <- Inter_Data %>% filter(!Subject %in% c("111", "112"))
```


# Checking sample size
```{r checking sample size}
## compute sample size for interpolated test data
Inter_Sample_Size <- Inter_Data %>%
  group_by(AgeGroup) %>%
  mutate(N = n_distinct(Subject)) %>%
  summarise(N = mean(N))
Inter_Sample_Size
```


# Create Binary Variables for interpolated accuracy and creating a data frame
```{r create binary variables for interpolated accuracy and creating a data frame}
## create binary variable for interpolated test accuracy
## target should match L1 response
Inter_Data$L1_Inter_Test_Acc <- ifelse(Inter_Data$Target == Inter_Data$L1TestItem.RESP, 1, 0)

## create data frame for interpolated item types
Inter_Data_df <- Inter_Data %>% 
  filter(ItemType %in% c("AB_AD_Test_FB", "AB_AD_Test")) %>%
  select(Subject, AgeGroup, Cue, ItemType, L1_Inter_Test_Acc)
Inter_Data_df
```


# Set Factors
```{r set factors}
Inter_Data_df %<>%
  mutate_at(c("Subject", "AgeGroup", "Cue", "ItemType"), factor)
```


# Fit Mixed Effects Model to Interpolated recall and Extract Estimated Probabilities
```{r fit mixed effects model to interpolated recall and extract estimated probabilities}
## fit model to interpolated test recall
Inter_Recall_glmer <- glmer(L1_Inter_Test_Acc ~ AgeGroup * ItemType + 
                              (1 | Subject) + (1 | Cue), 
                            family = binomial, 
                            data = Inter_Data_df)

## anova for interpolated test recall
Anova(Inter_Recall_glmer)

## pairwise comparisons
Inter_Recall_glmer_emmeans <- emmeans(Inter_Recall_glmer, pairwise ~ ItemType | AgeGroup, type = "response")
Inter_Recall_glmer_emmeans

## extract estimated probabilities
Inter_Recall_glmer_emmeans_df <- as_tibble(Inter_Recall_glmer_emmeans$emmeans)
Inter_Recall_glmer_emmeans_df
```


# Save the data frame
```{r save the data frame}
save(file="1911_Interpolated_Data.RData", Inter_Data_df)
```



# Calculating actual probabilities for interpolated accuracy
```{r Calculating actual probabilities for interpolated accuracy}
Inter_recall_df <- Inter_Data_df %>%
  group_by(AgeGroup, ItemType) %>%
  do(data.frame(rbind(smean.cl.boot(.$L1_Inter_Test_Acc, conf.int=.95, B=1000)))) %>%
  mutate_if(is.numeric, round, digits = 2)
Inter_recall_df
```


# Bar graph to show model estimated probabilities for List 1 recall in the interpolated phase
```{r Bar graph to show model estimated probabilities for List 1 recall in the interpolated phase, fig.height=4, fig.width=4}

# rearrange factor levels
Inter_Recall_glmer_emmeans_df$ItemType <- factor(Inter_Recall_glmer_emmeans_df$ItemType, levels = c("AB_AD_Test", "AB_AD_Test_FB"))
Inter_Recall_glmer_emmeans_df$AgeGroup <- factor(Inter_Recall_glmer_emmeans_df$AgeGroup, levels = c("Younger", "Older"))

# bar plot
Inter_Recall_plot <- ggplot(Inter_Recall_glmer_emmeans_df, aes(x = ItemType, y = prob, group = AgeGroup)) +
  geom_bar(aes(fill = AgeGroup), color = "black", stat = "identity", position = "dodge", size = .5, width = .45) +
  geom_errorbar(aes(ymin = asymp.LCL, ymax = asymp.UCL), color = "black", position = position_dodge(width = .45), width = 0.1, 
                size = .5,show.legend = FALSE) +
  scale_x_discrete(labels=c("AB_AD_Test" = "Test", "AB_AD_Test_FB" = "Test FB")) +
  scale_y_continuous(expand = c(0, 0), limits = c(0, 1), breaks = seq(0, 1, .1)) +
  scale_fill_manual("AgeGroup", values = c("Younger" = "Grey", "Older" = "white"), labels = c("Younger", "Older")) +
  xlab("Item Type") +
  ylab("Interpolated Recall") +
  ggtitle("Interpolated List 1 Recall") +
  theme(legend.position = c(0.02, -0.10),
    legend.direction ="horizontal",
    legend.key.size = unit(.4, "cm"),
    legend.key=element_rect(color = "black", size = .2),
    legend.title=element_blank(),
    legend.text=element_text(size = 6),
    strip.background=element_blank(),
    strip.text.y=element_blank(),
    axis.ticks.x=element_blank(),  
    axis.ticks.y=element_line(size=.3,color="black"),
    axis.text.x=element_text(size=8,color="black"),
    axis.text.y=element_text(size=8,color="black"),    
    axis.title.y=element_text(size=10, margin = margin(0, 8, 0, 0)),
    plot.title = element_text(size = 10, color = "black", hjust = .5), 
    panel.background = element_blank(),
    panel.border = element_rect(size = .5, fill = NA, color = "black"))  
Inter_Recall_plot

ggsave("Inter_Recall_plot.png", plot = Inter_Recall_plot, width = 4, height = 4, units = "in", dpi = 320)

```