---
title: "1911_Figures"
author: "Paige Kemp"
date: "29/10/2021"
output: html_document
---

# Clear Environment and Load Packages
```{r clear Environment and load packages}
## clear environment
rm(list=ls())

## load packages
library(tidyverse)
library(magrittr)
library(lme4)
library(car)
library(emmeans)
library(see)
library(dplyr)

## turn off scientific notation
options(scipen = 999)
```

# Load/Read data
```{r load/read data}
## load interpolated data
load("1911_Interpolated_Data.Rdata")

## read test data
Test_Data <- read.csv("1911_Test_data.csv", stringsAsFactors = FALSE, fileEncoding="UTF-8-BOM")

## exclude subjects
Test_Data <- Test_Data %>% filter(!Subject %in% c("111", "112"))

## replace m response with 0
Test_Data$CR.RESP <- ifelse(Test_Data$CR.RESP == "m", 0 , 
                     ifelse(Test_Data$CR.RESP == 1, 1, Test_Data$CR.RESP))
```

# Create Binary Variables for List Accuracies, Change Classifications, and Create a Data Frame
```{r create binary variables for list accuracies, change classifications, and create a data frame}
## create a binary variables for test responses
## list 2 accuracy
## Target should match test response
Test_Data$L2_Test_Acc <- ifelse(Test_Data$Target == Test_Data$TestItem.RESP, 1, 0)

## list 1 accuracy
## Alternate should match other response
Test_Data$L1_Test_Acc <- ifelse(Test_Data$Alternate == Test_Data$OtherResp.RESP, 1, 0)

## list 1 intrusions on list 2 test
## Alternate should match test response
Test_Data$L1_Intrusion <- ifelse(Test_Data$Alternate == Test_Data$TestItem.RESP, 1, 0)

## create variable for change classification response
Test_Data$Change_Class <- ifelse(Test_Data$CR.RESP == 1 & Test_Data$L1_Test_Acc == 1, "Change Recollected",
                          ifelse(Test_Data$CR.RESP == 1 & Test_Data$L1_Test_Acc == 0, "Change Remembered (Not Recollected)",
                          ifelse(Test_Data$CR.RESP == 0, "Change Not Remembered", "")))

## create binary variables for change classification responses
Test_Data$ChangeRecollected <- ifelse(Test_Data$Change_Class == "Change Recollected", 1, 0)

## Test_Data$ChangeRemembered <- ifelse(Test_Data$Change_Class == "Change Remembered (Not Recollected)", 1, 0)
## Test_Data$ChangeNotRemembered <- ifelse(Test_Data$Change_Class == "Change Not Remembered", 1, 0)

Test_Data$ChangeRecollected_Fig <- ifelse(Test_Data$Change_Class == "Change Recollected", "Recollected", "Not Recollected")

## dropping subtrial from data frame
Test_Data_df <- Test_Data %>% 
  select(-SubTrial)
Test_Data_df

## set factors
Test_Data_df %<>%
  mutate_at(c("Subject", "AgeGroup", "Cue", "ItemType", "ChangeRecollected_Fig", "Change_Class"), factor)
Test_Data_df
```

# Set Global Variables
```{r set global variables}
## set global variables
more_control <- glmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 2e4))
```


# Joining/Creating data frames
```{r joining/creating data frames}
## join interpolated and test data frames
Data_All <- Inter_Data_df %>% full_join(Test_Data_df, by = c("Subject", "AgeGroup", "Cue", "ItemType"))

## create data frame with the repeated items dropped
Data_No_Repeated_df <-Data_All %>% filter(!ItemType == "AB_AB") %>% droplevels

## create data frame with only the changed items
Data_Only_Changed_df <- Data_All %>% filter(ItemType %in% c("AB_AD", "AB_AD_Test", "AB_AD_Test_FB")) %>% droplevels

## set factors
Data_All %<>% mutate_at(("ItemType"), factor)
Data_No_Repeated_df %<>% mutate_at(("ItemType"), factor)
Data_Only_Changed_df %<>% mutate_at(("ItemType"), factor)
```

# Final Cued Recall Test: List 2 Recall and List 1 Intrusions 
# Fit Mixed Effects Model to List 2 Recall and Extract Estimated Probabilities
```{r fit mixed effects model to list 2 recall and extract estimated probabilities}
## fit model to list 2 recall
L2_Recall_glmer <- glmer(L2_Test_Acc ~ AgeGroup * ItemType + 
                           (1 | Subject) + (1 | Cue), 
                         family = binomial, 
                         data = Data_No_Repeated_df)

## summary for List 2 recall
summary(L2_Recall_glmer)

## anova for List 2 recall
Anova(L2_Recall_glmer)

## pairwise comparisons
L2_Recall_glmer_emmeans <- emmeans(L2_Recall_glmer, 
                                   list(pairwise ~ AgeGroup,
                                        pairwise ~ ItemType,
                                        pairwise ~ ItemType | AgeGroup), type = "response")
L2_Recall_glmer_emmeans

## extract estimated probabilities
L2_Recall_glmer_emmeans_df <- as_tibble(L2_Recall_glmer_emmeans$`emmeans of ItemType | AgeGroup`)
L2_Recall_glmer_emmeans_df
```

# Create Data Frames For List 2 Visualization
```{r create data Frames for list 2 visualization}
## data frame for individual subjects data
Data_No_Repeated_Sub_df <- Data_No_Repeated_df %>% 
  group_by(AgeGroup, Subject, ItemType) %>% 
  summarise(List2Recall = mean(L2_Test_Acc), 
            List1Intrusion = mean(L1_Intrusion))

## lowered and raised data points for later visualization
Data_No_Repeated_Sub_df$List2Recall <- ifelse(Data_No_Repeated_Sub_df$List2Recall == 1, .99,
                                       ifelse(Data_No_Repeated_Sub_df$List2Recall == 0, .01,
                                              Data_No_Repeated_Sub_df$List2Recall))

Data_No_Repeated_Sub_df$List1Intrusion <- ifelse(Data_No_Repeated_Sub_df$List1Intrusion == 1, .99,
                                          ifelse(Data_No_Repeated_Sub_df$List1Intrusion == 0, .01,
                                                 Data_No_Repeated_Sub_df$List1Intrusion))
                                              
## reorder factor levels
Data_No_Repeated_Sub_df$ItemType <- factor(Data_No_Repeated_Sub_df$ItemType, levels = c("AB_CD", "AB_AD", "AB_AD_Test", "AB_AD_Test_FB"))
Data_No_Repeated_Sub_df$AgeGroup <- factor(Data_No_Repeated_Sub_df$AgeGroup, levels = c("Younger", "Older"))

## set x axis position for point plots
Data_No_Repeated_Sub_df$x_pos_pnt <- ifelse(Data_No_Repeated_Sub_df$ItemType == "AB_CD", .95,
                                     ifelse(Data_No_Repeated_Sub_df$ItemType == "AB_AD", 1.95, 
                                     ifelse(Data_No_Repeated_Sub_df$ItemType == "AB_AD_Test", 2.95,        
                                     ifelse(Data_No_Repeated_Sub_df$ItemType == "AB_AD_Test_FB", 3.95, "")))) %>% as.numeric()

## set x axis position for violin plots
Data_No_Repeated_Sub_df$x_pos_vio <- ifelse(Data_No_Repeated_Sub_df$ItemType == "AB_CD", 1.05,
                                     ifelse(Data_No_Repeated_Sub_df$ItemType == "AB_AD", 2.05, 
                                     ifelse(Data_No_Repeated_Sub_df$ItemType == "AB_AD_Test", 3.05,        
                                     ifelse(Data_No_Repeated_Sub_df$ItemType == "AB_AD_Test_FB", 4.05, "")))) %>% as.numeric()

## set x axis position for x position mean plots
Data_No_Repeated_Sub_df$x_pos_mean <- ifelse(Data_No_Repeated_Sub_df$ItemType == "AB_CD", 1.04,
                                      ifelse(Data_No_Repeated_Sub_df$ItemType == "AB_AD", 2.04, 
                                      ifelse(Data_No_Repeated_Sub_df$ItemType == "AB_AD_Test", 3.04,        
                                      ifelse(Data_No_Repeated_Sub_df$ItemType == "AB_AD_Test_FB", 4.04, "")))) %>% as.numeric()

## set x axis position for x position mean plots
L2_Recall_glmer_emmeans_df$x_pos_mean <- ifelse(L2_Recall_glmer_emmeans_df$ItemType == "AB_CD", 1.1,
                                         ifelse(L2_Recall_glmer_emmeans_df$ItemType == "AB_AD", 2.1, 
                                         ifelse(L2_Recall_glmer_emmeans_df$ItemType == "AB_AD_Test", 3.1,        
                                         ifelse(L2_Recall_glmer_emmeans_df$ItemType == "AB_AD_Test_FB", 4.1, "")))) %>% as.numeric()

```

# Plot Individual Subject Data For Overall Correct Recall
```{r plot individual subject data for overall correct recall, fig.height=4, fig.width=8}
correct_sub_p <- ggplot(Data_No_Repeated_Sub_df, aes(x = ItemType, y = List2Recall, fill = ItemType)) +
  geom_violinhalf(aes(x = x_pos_pnt), scale = "count") +
  geom_dotplot(aes(fill = ItemType, x = x_pos_pnt), method = "dotdensity", binaxis = "y", stackdir = "down", dotsize = .5, stackratio = .8) +
  stat_summary(aes(x = x_pos_mean), geom = "errorbar", fun.data = "mean_cl_boot", width = 0, size = 1) +
  stat_summary(aes(x = x_pos_mean), geom = "point", fun.y = "mean", shape = 21, size = 3, fill = "black") +
  geom_segment(data = L2_Recall_glmer_emmeans_df, 
               aes(x = x_pos_mean, xend = x_pos_mean, y = asymp.LCL, yend = asymp.UCL),  color = "black", size = 1) + 
  geom_point(data = L2_Recall_glmer_emmeans_df, 
             aes(x = x_pos_mean, y = prob), shape = 23, size = 3,  color = "black", fill = "white") +
  facet_grid(. ~ AgeGroup) +
  scale_fill_manual (values = c("gray100","gray80", "gray60", "gray40")) +
  scale_x_continuous(breaks=seq(1, 4, 1), limits = c(0.5, 4.5), labels = c("A-B, C-D", "A-B, A-D", "A-B, A-D\nTested", "A-B, A-D\nTested\nFeedback")) +
  scale_y_continuous(expand = c(0, 0), limits = c(-0.05, 1.1), breaks = seq(0, 1, .1)) +
  labs(x = "Item Type", y = "List 2 Recall") +
  theme(legend.position = "none",
        legend.key.size = unit(.65, "cm"),
        legend.key=element_rect(color = "black", size = .1),     
        legend.title=element_blank(),
        legend.text=element_blank(),
        strip.background=element_blank(),
        strip.text.x=element_text(size = 16, color = "black", margin = margin(0, 0, 8, 0)),
        strip.text.y=element_blank(),
        axis.ticks.x=element_blank(),
        axis.ticks.y=element_line(size=.3,color="black"),
        axis.text.x=element_text(size=12,color="black"),
        axis.text.y=element_text(size=11,color="black"),
        axis.title.x=element_text(size=16, margin = margin(8, 0, 0, 0), hjust = .5),
        axis.title.y=element_text(size=16, margin = margin(0, 8, 0, 0)),
        plot.margin = unit(c(.15, .15, .15, .15), "in"),
        plot.title = element_text(size = 18, color = "black", hjust = 0, vjust = 3), 
        panel.background = element_blank(),
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
        panel.spacing = unit(-0.01, "cm"),
        panel.border = element_rect(size = .5, fill = NA, color = "black"))
correct_sub_p

# ggsave("correct_sub_p.png", plot = correct_sub_p, width = 8, height = 4, units = "in", dpi = 320)

```


# Fit Mixed Effects Model to List 1 Intrusions and Extract Estimated Probabilities
```{r fit mixed effects model to list 1 intrusions and extract estimated probabilities}
## fit model to list 1 intrusions
L1_Intru_glmer <- glmer(L1_Intrusion ~ AgeGroup * ItemType + 
                          (1 | Subject) + (1 | Cue),  
                        family = binomial, 
                        data = Data_No_Repeated_df)

## summary for list 1 intrusions
summary(L1_Intru_glmer)

## anova for list 1 intrusions
Anova(L1_Intru_glmer)

## pairwise comparisons
L1_Intru_glmer_emmeans <- emmeans(L1_Intru_glmer, 
                                   list(pairwise ~ AgeGroup,
                                        pairwise ~ ItemType,
                                        pairwise ~ ItemType | AgeGroup), type = "response")
L1_Intru_glmer_emmeans

## extract estimated probabilities
L1_Intru_glmer_emmeans_df <- as_tibble(L1_Intru_glmer_emmeans$`emmeans of ItemType | AgeGroup`)
L1_Intru_glmer_emmeans_df

## drop control items for visualization
L1_Intru_glmer_emmeans_df %<>% filter(ItemType != "AB_CD") 
L1_Intru_glmer_emmeans_df
```


# Alterations For List 1 Intrusions Visualization
```{r alterations for list 1 intrusions visualization}
## data frame for only changed item types 
Data_AB_AD_Only_Sub_df <- Data_No_Repeated_Sub_df %>%filter(ItemType != "AB_CD")
Data_AB_AD_Only_Sub_df

## set x axis position for x position mean plots
L1_Intru_glmer_emmeans_df$x_pos_mean <- ifelse(L1_Intru_glmer_emmeans_df$ItemType == "AB_AD", 1.1, 
                                        ifelse(L1_Intru_glmer_emmeans_df$ItemType == "AB_AD_Test", 2.1,        
                                        ifelse(L1_Intru_glmer_emmeans_df$ItemType == "AB_AD_Test_FB", 3.1, ""))) %>% as.numeric()

## set x axis position for point plots
Data_AB_AD_Only_Sub_df$x_pos_pnt <- ifelse(Data_AB_AD_Only_Sub_df$ItemType == "AB_AD", .95,
                                    ifelse(Data_AB_AD_Only_Sub_df$ItemType == "AB_AD_Test", 1.95, 
                                    ifelse(Data_AB_AD_Only_Sub_df$ItemType == "AB_AD_Test_FB", 2.95, ""))) %>% as.numeric()

## set x axis position for violin plots
Data_AB_AD_Only_Sub_df$x_pos_vio <- ifelse(Data_AB_AD_Only_Sub_df$ItemType == "AB_AD", 1.05,
                                    ifelse(Data_AB_AD_Only_Sub_df$ItemType == "AB_AD_Test", 2.05, 
                                    ifelse(Data_AB_AD_Only_Sub_df$ItemType == "AB_AD_Test_FB", 3.05, ""))) %>% as.numeric()

## set x axis position for x position mean plots
Data_AB_AD_Only_Sub_df$x_pos_mean <- ifelse(Data_AB_AD_Only_Sub_df$ItemType == "AB_AD", 1.04,
                                     ifelse(Data_AB_AD_Only_Sub_df$ItemType == "AB_AD_Test", 2.04, 
                                     ifelse(Data_AB_AD_Only_Sub_df$ItemType == "AB_AD_Test_FB", 3.04, ""))) %>% as.numeric()
```


# Plot Individual Subject Data For Overall List 1 Intrusions 
```{r plot individual subject data for overall list 1 intrusions, fig.height=4, fig.width=8}
intrusions_sub_p <- ggplot(Data_AB_AD_Only_Sub_df, aes(x = ItemType, y = List1Intrusion, fill = ItemType)) +
  geom_violinhalf(aes(x = x_pos_pnt), scale = "count") +
  geom_dotplot(aes(fill = ItemType, x = x_pos_pnt), method = "dotdensity", binaxis = "y", stackdir = "down", dotsize = .5, stackratio = .8) +
  stat_summary(aes(x = x_pos_mean), geom = "errorbar", fun.data = "mean_cl_boot", width = 0, size = 1) +
  stat_summary(aes(x = x_pos_mean), geom = "point", fun.y = "mean", shape = 21, size = 3, fill = "black") +
  geom_segment(data = L1_Intru_glmer_emmeans_df, 
               aes(x = x_pos_mean, xend = x_pos_mean, y = asymp.LCL, yend = asymp.UCL),  color = "black", size = 1) + 
  geom_point(data = L1_Intru_glmer_emmeans_df, 
             aes(x = x_pos_mean, y = prob), shape = 23, size = 3,  color = "black", fill = "white") +
  facet_grid(. ~ AgeGroup) +
  scale_fill_manual (values = c("gray80", "gray60", "gray40")) +
  scale_x_continuous(breaks=seq(1, 3, 1), limits = c(0.5, 3.5), labels = c("A-B, A-D", "A-B, A-D\nTested", "A-B, A-D\nTested\nFeedback")) +
  scale_y_continuous(expand = c(0, 0), limits = c(-0.05, 1), breaks = seq(0, 1, .1)) +
  labs(x = "Item Type", y = "List 1 Intrusions") +
  theme(legend.position = "none",
        legend.key.size = unit(.65, "cm"),
        legend.key=element_rect(color = "black", size = .1),     
        legend.title=element_blank(),
        legend.text=element_blank(),
        strip.background=element_blank(),
        strip.text.x=element_text(size = 16, color = "black", margin = margin(0, 0, 8, 0)),
        strip.text.y=element_blank(),
        axis.ticks.x=element_blank(),
        axis.ticks.y=element_line(size=.3,color="black"),
        axis.text.x=element_text(size=12,color="black"),
        axis.text.y=element_text(size=11,color="black"),
        axis.title.x=element_text(size=16, margin = margin(8, 0, 0, 0), hjust = .5),
        axis.title.y=element_text(size=16, margin = margin(0, 8, 0, 0)),
        plot.margin = unit(c(.15, .15, .15, .15), "in"),
        plot.title = element_text(size = 18, color = "black", hjust = 0, vjust = 3), 
        panel.background = element_blank(),
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
        panel.spacing = unit(-0.01, "cm"),
        panel.border = element_rect(size = .5, fill = NA, color = "black"))
intrusions_sub_p

# ggsave("intrusions_sub_p.png", plot = intrusions_sub_p, width = 8, height = 4, units = "in", dpi = 320)
```

# Fit Mixed Effects Model to List 2 Recall Conditionalized on Change Classifications
```{r fit mixed effects model to list 2 recall conditionalized on change classifications}
## fit model to list 2 recall accuracy conditionalized on change classification
L2_Recall_Cond_glmer <- glmer(L2_Test_Acc ~ AgeGroup * ItemType * Change_Class +
                              (1 | Subject) + (1 | Cue), 
                              family = binomial, 
                              control = more_control, 
                              data = Data_Only_Changed_df)

## Anova for List 2 recall accuracy conditionalized on change classification
Anova(L2_Recall_Cond_glmer)

## Summary for List 2 recall accuracy conditionalized on change classification
summary(L2_Recall_Cond_glmer)

## pairwise comparisons
L2_Recall_Cond_glmer_emmeans <- emmeans(L2_Recall_Cond_glmer, 
                                        list(pairwise ~ AgeGroup,
                                             pairwise ~ Change_Class,
                                             pairwise ~ AgeGroup | Change_Class,
                                             pairwise ~ ItemType | Change_Class,
                                             pairwise ~ ItemType | AgeGroup | Change_Class), type = "response")
L2_Recall_Cond_glmer_emmeans

## extract estimated probabilities
L2_Recall_Cond_glmer_emmeans_df <- as_tibble(L2_Recall_Cond_glmer_emmeans$emmeans)
L2_Recall_Cond_glmer_emmeans_df
```


# Combine Data Frames for Change Class
```{r combine data frames for change class}
## summarize change classification responses
Change_Class_prop <- Data_Only_Changed_df %>% 
  group_by(AgeGroup, ItemType) %>%
  filter(ItemType %in% c("AB_AD", "AB_AD_Test", "AB_AD_Test_FB")) %>% 
  count(Change_Class) %>% 
  mutate(prop = n / sum(n)) %>%
  select(-n) %>%
  pivot_wider(names_from = Change_Class, values_from = prop) %>% 
  select(AgeGroup, ItemType, "Change Recollected", "Change Remembered (Not Recollected)", "Change Not Remembered") %>%
  arrange(desc(AgeGroup))
Change_Class_prop$Total <- rowSums(Change_Class_prop[, 3:4])
Change_Class_prop

## convert data frame to long format
Change_Class_prop_l <- Change_Class_prop %>% 
  select(-Total) %>%
  pivot_longer(cols = c("Change Recollected", "Change Remembered (Not Recollected)", "Change Not Remembered"), 
                 names_to = "Change_Class", values_to = "changeprob")
Change_Class_prop_l

# join change recollection and list 2 recollection data frames
List2_Recall_Cond <- L2_Recall_Cond_glmer_emmeans_df %>% 
  left_join(Change_Class_prop_l)
List2_Recall_Cond

L2_Recall_glmer_emmeans_df$Change_Class <- "All"
L2_Recall_glmer_emmeans_df$changeprob <- "1"

L2_Recall_glmer_emmeans_df <- L2_Recall_glmer_emmeans_df %>% select(-x_pos_mean)

# Bind data frames
List2_Recall_bubble_df <- rbind(List2_Recall_Cond, L2_Recall_glmer_emmeans_df)
List2_Recall_bubble_df
```


# Alterations For List 2 Recall Conditionalized
```{r alterations for list 2 recall conditionalized}
# Set x position for probabilities and confidence intervals
List2_Recall_bubble_df$x_pnt_pos <- 
  ifelse(List2_Recall_bubble_df$ItemType == "AB_CD", 1, 
  ifelse(List2_Recall_bubble_df$ItemType == "AB_AD"
       & List2_Recall_bubble_df$Change_Class == "All", 2, 
  ifelse(List2_Recall_bubble_df$ItemType == "AB_AD"
       & List2_Recall_bubble_df$Change_Class == "Change Recollected", 3,
  ifelse(List2_Recall_bubble_df$ItemType == "AB_AD"
       & List2_Recall_bubble_df$Change_Class == "Change Remembered (Not Recollected)", 2.75,
  ifelse(List2_Recall_bubble_df$ItemType == "AB_AD"
       & List2_Recall_bubble_df$Change_Class == "Change Not Remembered", 3,
  ifelse(List2_Recall_bubble_df$ItemType == "AB_AD_Test"
       & List2_Recall_bubble_df$Change_Class == "All", 4, 
  ifelse(List2_Recall_bubble_df$ItemType == "AB_AD_Test"
       & List2_Recall_bubble_df$Change_Class == "Change Recollected", 5,
  ifelse(List2_Recall_bubble_df$ItemType == "AB_AD_Test"
       & List2_Recall_bubble_df$Change_Class == "Change Remembered (Not Recollected)", 4.75,
  ifelse(List2_Recall_bubble_df$ItemType == "AB_AD_Test"
       & List2_Recall_bubble_df$Change_Class == "Change Not Remembered", 5,    
  ifelse(List2_Recall_bubble_df$ItemType == "AB_AD_Test_FB"
       & List2_Recall_bubble_df$Change_Class == "All", 6, 
  ifelse(List2_Recall_bubble_df$ItemType == "AB_AD_Test_FB"
       & List2_Recall_bubble_df$Change_Class == "Change Recollected", 7,
  ifelse(List2_Recall_bubble_df$ItemType == "AB_AD_Test_FB"
       & List2_Recall_bubble_df$Change_Class == "Change Remembered (Not Recollected)", 6.75,
  ifelse(List2_Recall_bubble_df$ItemType == "AB_AD_Test_FB"
       & List2_Recall_bubble_df$Change_Class == "Change Not Remembered", 7, "") %>% as.numeric()))))))))))))

# add x position values to data frame for error bars
List2_Recall_bubble_df$x_pos_eb <- 
  ifelse(List2_Recall_bubble_df$ItemType == "AB_CD", 1, 
  ifelse(List2_Recall_bubble_df$ItemType == "AB_AD"
       & List2_Recall_bubble_df$Change_Class == "All", 2, 
  ifelse(List2_Recall_bubble_df$ItemType == "AB_AD"
       & List2_Recall_bubble_df$Change_Class == "Change Recollected", 3,
  ifelse(List2_Recall_bubble_df$ItemType == "AB_AD"
       & List2_Recall_bubble_df$Change_Class == "Change Remembered (Not Recollected)", 2.75,
  ifelse(List2_Recall_bubble_df$ItemType == "AB_AD"
       & List2_Recall_bubble_df$Change_Class == "Change Not Remembered", 3,
  ifelse(List2_Recall_bubble_df$ItemType == "AB_AD_Test"
       & List2_Recall_bubble_df$Change_Class == "All", 4, 
  ifelse(List2_Recall_bubble_df$ItemType == "AB_AD_Test"
       & List2_Recall_bubble_df$Change_Class == "Change Recollected", 5,
  ifelse(List2_Recall_bubble_df$ItemType == "AB_AD_Test"
       & List2_Recall_bubble_df$Change_Class == "Change Remembered (Not Recollected)", 4.75,
  ifelse(List2_Recall_bubble_df$ItemType == "AB_AD_Test"
       & List2_Recall_bubble_df$Change_Class == "Change Not Remembered", 5,    
  ifelse(List2_Recall_bubble_df$ItemType == "AB_AD_Test_FB"
       & List2_Recall_bubble_df$Change_Class == "All", 6, 
  ifelse(List2_Recall_bubble_df$ItemType == "AB_AD_Test_FB"
       & List2_Recall_bubble_df$Change_Class == "Change Recollected", 7,
  ifelse(List2_Recall_bubble_df$ItemType == "AB_AD_Test_FB"
       & List2_Recall_bubble_df$Change_Class == "Change Remembered (Not Recollected)", 6.75,
  ifelse(List2_Recall_bubble_df$ItemType == "AB_AD_Test_FB"
       & List2_Recall_bubble_df$Change_Class == "Change Not Remembered", 7, "") %>% as.numeric()))))))))))))
```

```{r Plot List 2 recall conditionalized on correction recollection, fig.height=4, fig.width=8}
# Plot List 2 recall conditionalized on correction recollection
List2_Recall_bubble_df_p <- List2_Recall_bubble_df %>% 
  ggplot(aes(x = ItemType, y = prob, color = Change_Class)) +
  geom_errorbar(aes(ymin = asymp.LCL, ymax = asymp.UCL, x = x_pos_eb), 
                  position=position_dodge(), size = .3, width = 0, colour="black", show.legend = FALSE) +
  geom_point(aes(size = changeprob, x = x_pnt_pos, fill = Change_Class), 
             color = "black", shape = 21, show.legend = FALSE) +
  scale_linetype_identity() +
  facet_grid( ~ AgeGroup) +
  scale_fill_manual(values=c("All" = "black",  "Change Recollected" = "springgreen3", "Change Remembered (Not Recollected)" = "blue", "Change Not Remembered" = "red")) + 
  scale_x_continuous(breaks=seq(1, 7, 1), limits = c(0.75, 7.25),
                     labels=c("A-B, C-D", 
                              "A-B, A-D", 
                              " ",
                              "A-B, A-D\nTested", 
                              " ",
                              "A-B, A-D\nTested\nFeedback",
                              " ")) +
 scale_y_continuous(name = "List 2 Recall", limits = c(0, 1.03), breaks = seq(0, 1, .1)) +
  labs(x = "Item Type") +
  theme(legend.key=element_rect(fill="transparent",size=0),
        legend.key.height=unit(1.2,"cm"),
        legend.key.width=unit(.8,"cm"),
        legend.text=element_text(size=10),
        strip.background=element_blank(),
        strip.text.x = element_text(size = 10, color = "black",margin = margin(0, 0, 8, 0)),
        strip.text.y = element_text(size = 10, color = "black", margin = margin(0,0,0,8)),
        axis.ticks.x = element_line(size = .3),
        axis.ticks.y = element_line(size = .3),
        axis.text.x = element_text(size = 8, color="black"),
        axis.text.y = element_text(size = 10, color="black"),
        axis.title.x = element_text(size = 12, margin = margin(8, 0, 0, 0)),
        axis.title.y = element_text(size = 12, margin = margin(0, 8, 0, 0)),
        panel.background = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.major.x = element_blank(),
        panel.grid.minor = element_blank(),
        panel.spacing = unit(-0.0001, "cm"),
        panel.border = element_rect(size = .3, fill = NA, color = "black"))
List2_Recall_bubble_df_p

ggsave("List2_Recall_bubble_df_p.png", plot = List2_Recall_bubble_df_p, width = 10, height = 4, units = "in", dpi = 320)
```

# Fit Mixed Effects Model to List 1 Intrusions Conditionalized and Extract Estimated Probabilities
```{r fit mixed effects model to list 1 intrusions conditionalized and extract estimated probabilities}
# fit model to list 1 intrusions
L1_Intru_Cond_glmer <- glmer(L1_Intrusion ~ AgeGroup * ItemType * Change_Class 
                             + (1 | Subject) + (1 | Cue), 
                             family = binomial, 
                             control = more_control, 
                             data = Data_Only_Changed_df)

# Anova for list 1 intrusions
Anova(L1_Intru_Cond_glmer)

# Summary for list 1 intrusions
summary(L1_Intru_Cond_glmer)

## pairwise comparisons
L1_Intru_Cond_glmer_emmeans <- emmeans(L1_Intru_Cond_glmer, 
                                list(pairwise ~ ItemType,
                                     pairwise ~ Change_Class,
                                     pairwise ~ ItemType | AgeGroup | Change_Class), type = "response")
L1_Intru_Cond_glmer_emmeans

## extract estimated probabilities
L1_Intru_Cond_glmer_emmeans_df <- as_tibble(L1_Intru_Cond_glmer_emmeans$emmeans)
L1_Intru_Cond_glmer_emmeans_df %<>% select(-df) %>% mutate_if(is.numeric, round, digits = 3)
L1_Intru_Cond_glmer_emmeans_df
```

# Combine data frames
```{r combine data frames}
# join change recollection and list 1 intrusions data frames
List1_Intru_Cond <- L1_Intru_Cond_glmer_emmeans_df %>% 
  left_join(Change_Class_prop_l)
List1_Intru_Cond

L1_Intru_glmer_emmeans_df$Change_Class <- "All"
L1_Intru_glmer_emmeans_df$changeprob <- "1"

L1_Intru_glmer_emmeans_df <-  L1_Intru_glmer_emmeans_df %>% select(-x_pos_mean, -df)
# Bind data frames
List1_Recall_bubble_df <- rbind(List1_Intru_Cond, L1_Intru_glmer_emmeans_df)
List1_Recall_bubble_df

```

# Alterations For List 1 Intrusions Conditionalized
```{r alterations for list 1 Intrusions conditionalized}
# Set x position for probabilities and confidence intervals
List1_Recall_bubble_df$x_pnt_pos <- 
  ifelse(List1_Recall_bubble_df$ItemType == "AB_AD"
       & List1_Recall_bubble_df$Change_Class == "All", 1, 
  ifelse(List1_Recall_bubble_df$ItemType == "AB_AD"
       & List1_Recall_bubble_df$Change_Class == "Change Recollected", 2,
  ifelse(List1_Recall_bubble_df$ItemType == "AB_AD"
       & List1_Recall_bubble_df$Change_Class == "Change Remembered (Not Recollected)", 1.75,
  ifelse(List1_Recall_bubble_df$ItemType == "AB_AD"
       & List1_Recall_bubble_df$Change_Class == "Change Not Remembered", 2,
  ifelse(List1_Recall_bubble_df$ItemType == "AB_AD_Test"
       & List1_Recall_bubble_df$Change_Class == "All", 3, 
  ifelse(List1_Recall_bubble_df$ItemType == "AB_AD_Test"
       & List1_Recall_bubble_df$Change_Class == "Change Recollected", 4,
  ifelse(List1_Recall_bubble_df$ItemType == "AB_AD_Test"
       & List1_Recall_bubble_df$Change_Class == "Change Remembered (Not Recollected)", 3.75,
  ifelse(List1_Recall_bubble_df$ItemType == "AB_AD_Test"
       & List1_Recall_bubble_df$Change_Class == "Change Not Remembered", 4,    
  ifelse(List1_Recall_bubble_df$ItemType == "AB_AD_Test_FB"
       & List1_Recall_bubble_df$Change_Class == "All", 5, 
  ifelse(List1_Recall_bubble_df$ItemType == "AB_AD_Test_FB"
       & List1_Recall_bubble_df$Change_Class == "Change Recollected", 6,
  ifelse(List1_Recall_bubble_df$ItemType == "AB_AD_Test_FB"
       & List1_Recall_bubble_df$Change_Class == "Change Remembered (Not Recollected)", 5.75,
  ifelse(List1_Recall_bubble_df$ItemType == "AB_AD_Test_FB"
       & List1_Recall_bubble_df$Change_Class == "Change Not Remembered", 6, "") %>% as.numeric())))))))))))

# add x position values to data frame for error bars
List1_Recall_bubble_df$x_pos_eb <- 
  ifelse(List1_Recall_bubble_df$ItemType == "AB_AD"
       & List1_Recall_bubble_df$Change_Class == "All", 0.8, 
  ifelse(List1_Recall_bubble_df$ItemType == "AB_AD"
       & List1_Recall_bubble_df$Change_Class == "Change Recollected", 1.8,
  ifelse(List1_Recall_bubble_df$ItemType == "AB_AD"
       & List1_Recall_bubble_df$Change_Class == "Change Remembered (Not Recollected)", 1.75,
  ifelse(List1_Recall_bubble_df$ItemType == "AB_AD"
       & List1_Recall_bubble_df$Change_Class == "Change Not Remembered", 2,
  ifelse(List1_Recall_bubble_df$ItemType == "AB_AD_Test"
       & List1_Recall_bubble_df$Change_Class == "All", 2.8, 
  ifelse(List1_Recall_bubble_df$ItemType == "AB_AD_Test"
       & List1_Recall_bubble_df$Change_Class == "Change Recollected", 3.8,
  ifelse(List1_Recall_bubble_df$ItemType == "AB_AD_Test"
       & List1_Recall_bubble_df$Change_Class == "Change Remembered (Not Recollected)", 3.75,
  ifelse(List1_Recall_bubble_df$ItemType == "AB_AD_Test"
       & List1_Recall_bubble_df$Change_Class == "Change Not Remembered", 4,    
  ifelse(List1_Recall_bubble_df$ItemType == "AB_AD_Test_FB"
       & List1_Recall_bubble_df$Change_Class == "All", 4.8, 
  ifelse(List1_Recall_bubble_df$ItemType == "AB_AD_Test_FB"
       & List1_Recall_bubble_df$Change_Class == "Change Recollected", 5.8,
  ifelse(List1_Recall_bubble_df$ItemType == "AB_AD_Test_FB"
       & List1_Recall_bubble_df$Change_Class == "Change Remembered (Not Recollected)", 5.75,
  ifelse(List1_Recall_bubble_df$ItemType == "AB_AD_Test_FB"
       & List1_Recall_bubble_df$Change_Class == "Change Not Remembered", 6, "") %>% as.numeric())))))))))))
```

```{r Plot List 1 recall conditionalized on correction recollection, fig.height=4, fig.width=8}
# Plot List 1 recall conditionalized on correction recollection
List1_Recall_bubble_df_p <- List1_Recall_bubble_df %>% 
  ggplot(aes(x = ItemType, y = prob, color = Change_Class)) +
  geom_errorbar(aes(ymin = asymp.LCL, ymax = asymp.UCL, x = x_pos_eb), 
                  position=position_dodge(), size = .3, width = 0, colour="black", show.legend = FALSE) +
  geom_point(aes(size = changeprob, x = x_pnt_pos, fill = Change_Class), 
             color = "black", shape = 21, show.legend = FALSE) +
  scale_linetype_identity() +
  facet_grid( ~ AgeGroup) +
  scale_fill_manual(values=c("All" = "black",  "Change Recollected" = "springgreen3", "Change Remembered (Not Recollected)" = "blue", "Change Not Remembered" = "red")) + 
  scale_x_continuous(breaks=seq(1, 6, 1), limits = c(0.75, 6.25),
                     labels=c("A-B, A-D", 
                              " ",
                              "A-B, A-D\nTested", 
                              " ",
                              "A-B, A-D\nTested\nFeedback",
                              " ")) +
 scale_y_continuous(name = "List 1 Intrusions", limits = c(0, 1.03), breaks = seq(0, 1, .1)) +
  labs(x = "Item Type") +
  theme(legend.key=element_rect(fill="transparent",size=0),
        legend.key.height=unit(1.2,"cm"),
        legend.key.width=unit(.8,"cm"),
        legend.text=element_text(size=10),
        strip.background=element_blank(),
        strip.text.x = element_text(size = 10, color = "black",margin = margin(0, 0, 8, 0)),
        strip.text.y = element_text(size = 10, color = "black", margin = margin(0,0,0,8)),
        axis.ticks.x = element_line(size = .3),
        axis.ticks.y = element_line(size = .3),
        axis.text.x = element_text(size = 8, color="black"),
        axis.text.y = element_text(size = 10, color="black"),
        axis.title.x = element_text(size = 12, margin = margin(8, 0, 0, 0)),
        axis.title.y = element_text(size = 12, margin = margin(0, 8, 0, 0)),
        panel.background = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.major.x = element_blank(),
        panel.grid.minor = element_blank(),
        panel.spacing = unit(-0.0001, "cm"),
        panel.border = element_rect(size = .3, fill = NA, color = "black"))
List1_Recall_bubble_df_p

ggsave("List1_Recall_bubble_df_p.png", plot = List1_Recall_bubble_df_p, width = 10, height = 4, units = "in", dpi = 320)
```
