---
title: "1911_Test_Data"
author: "Paige Kemp & Chris Wahlheim"
Date: 12/19/2020
output:
  html_document:
   toc: true
   toc_float: true
  pdf_document: default
   
---

# Clear Environment and Load Packages
```{r clear Environment and load packages}
## clear environment
rm(list=ls())

## load packages
library(tidyverse)
library(magrittr)
library(lme4)
library(car)
library(emmeans)
library(see)
library(dplyr)

## turn off scientific notation
options(scipen = 999)
```


# Load/Read data
```{r load/read data}
## load interpolated data
load("1911_Interpolated_Data.Rdata")

## read test data
Test_Data <- read.csv("1911_Test_data.csv", stringsAsFactors = FALSE, fileEncoding="UTF-8-BOM")

## exclude subjects
Test_Data <- Test_Data %>% filter(!Subject %in% c("111", "112"))

## replace m response with 0
Test_Data$CR.RESP <- ifelse(Test_Data$CR.RESP == "m", 0 , 
                     ifelse(Test_Data$CR.RESP == 1, 1, Test_Data$CR.RESP))
```


# Checking Sample Size
```{r checking sample size}
## compute sample size for final test data
Test_Sample_Size <- Test_Data %>%
  group_by(AgeGroup) %>%
  mutate(N = n_distinct(Subject)) %>%
  summarise(N = mean(N))
Test_Sample_Size
```


# Create Binary Variables for List Accuracies, Change Classifications, and Create a Data Frame
```{r create binary variables for list accuracies, change classifications, and create a data frame}
## create a binary variables for test responses
## list 2 accuracy
## Target should match test response
Test_Data$L2_Test_Acc <- ifelse(Test_Data$Target == Test_Data$TestItem.RESP, 1, 0)

## list 1 accuracy
## Alternate should match other response
Test_Data$L1_Test_Acc <- ifelse(Test_Data$Alternate == Test_Data$OtherResp.RESP, 1, 0)

## list 1 intrusions on list 2 test
## Alternate should match test response
Test_Data$L1_Intrusion <- ifelse(Test_Data$Alternate == Test_Data$TestItem.RESP, 1, 0)

## create variable for change classification response
Test_Data$Change_Class <- ifelse(Test_Data$CR.RESP == 1 & Test_Data$L1_Test_Acc == 1, "Change Recollected",
                          ifelse(Test_Data$CR.RESP == 1 & Test_Data$L1_Test_Acc == 0, "Change Remembered (Not Recollected)",
                          ifelse(Test_Data$CR.RESP == 0, "Change Not Remembered", "")))

## create binary variables for change classification responses
Test_Data$ChangeRecollected <- ifelse(Test_Data$Change_Class == "Change Recollected", 1, 0)

## Test_Data$ChangeRemembered <- ifelse(Test_Data$Change_Class == "Change Remembered (Not Recollected)", 1, 0)
## Test_Data$ChangeNotRemembered <- ifelse(Test_Data$Change_Class == "Change Not Remembered", 1, 0)

Test_Data$ChangeRecollected_Fig <- ifelse(Test_Data$Change_Class == "Change Recollected", "Recollected", "Not Recollected")

## dropping subtrial from data frame
Test_Data_df <- Test_Data %>% 
  select(-SubTrial)
Test_Data_df

## set factors
Test_Data_df %<>%
  mutate_at(c("Subject", "AgeGroup", "Cue", "ItemType", "ChangeRecollected_Fig", "Change_Class"), factor)
Test_Data_df
```


# Set Global Variables
```{r set global variables}
## set global variables
more_control <- glmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 2e4))
```


# Joining/Creating data frames
```{r joining/creating data frames}
## join interpolated and test data frames
Data_All <- Inter_Data_df %>% full_join(Test_Data_df, by = c("Subject", "AgeGroup", "Cue", "ItemType"))

## create data frame with the repeated items dropped
Data_No_Repeated_df <-Data_All %>% filter(!ItemType == "AB_AB") %>% droplevels

## create data frame with only the changed items
Data_Only_Changed_df <- Data_All %>% filter(ItemType %in% c("AB_AD", "AB_AD_Test", "AB_AD_Test_FB")) %>% droplevels

## set factors
Data_All %<>% mutate_at(("ItemType"), factor)
Data_No_Repeated_df %<>% mutate_at(("ItemType"), factor)
Data_Only_Changed_df %<>% mutate_at(("ItemType"), factor)
```


# Forward Difference Coding For List 2 Recall
```{r forward difference coding for list 2 recall}
## re-ordering factor levels for forward difference contrasts
Data_No_Repeated_df$ItemType <- factor(Data_No_Repeated_df$ItemType, levels = c("AB_CD", "AB_AD", "AB_AD_Test", "AB_AD_Test_FB"))
Data_No_Repeated_df$AgeGroup <- factor(Data_No_Repeated_df$AgeGroup, levels = c("Younger", "Older"))

## forward difference for factor variable with 2 Age levels
## using "contr.sum" to add to make levels sum to 0
contrasts(Data_No_Repeated_df$AgeGroup)<-"contr.sum"
contrasts(Data_No_Repeated_df$AgeGroup) 

## forward difference for factor variable with 4 Item Type levels
## making control items the reference
Data_No_Repeated_df$ItemType <- relevel(Data_No_Repeated_df$ItemType, ref="AB_CD")

## stating the contrasts
contrasts(Data_No_Repeated_df$ItemType)[,1] <- c(3/4,-1/4,-1/4,-1/4)
contrasts(Data_No_Repeated_df$ItemType)[,2] <- c(1/2,1/2,-1/2,-1/2)
contrasts(Data_No_Repeated_df$ItemType)[,3] <- c(1/4,1/4,1/4,-3/4)

## renaming the columns to clarify the contrasts
colnames(contrasts(Data_No_Repeated_df$ItemType)) <- c("AB_CD_vs_AB_AD", 
                                                    "AB_AD_vs_AB_AD_Test", 
                                                    "AB_AD_Test_vs_AB_AD_Test_FB")

## look at the final contrast matrix
contrasts(Data_No_Repeated_df$ItemType)
```


# Final Cued Recall Test: List 2 Recall and List 1 Intrusions 
# Fit Mixed Effects Model to List 2 Recall and Extract Estimated Probabilities
```{r fit mixed effects model to list 2 recall and extract estimated probabilities}
## fit model to list 2 recall
L2_Recall_glmer <- glmer(L2_Test_Acc ~ AgeGroup * ItemType + 
                           (1 | Subject) + (1 | Cue), 
                         family = binomial, 
                         data = Data_No_Repeated_df)

## summary for List 2 recall
summary(L2_Recall_glmer)

## anova for List 2 recall
Anova(L2_Recall_glmer)

## pairwise comparisons
L2_Recall_glmer_emmeans <- emmeans(L2_Recall_glmer, 
                                   list(pairwise ~ AgeGroup,
                                        pairwise ~ ItemType,
                                        pairwise ~ ItemType | AgeGroup), type = "response")
L2_Recall_glmer_emmeans

## extract estimated probabilities
L2_Recall_glmer_emmeans_df <- as_tibble(L2_Recall_glmer_emmeans$`emmeans of ItemType | AgeGroup`)
L2_Recall_glmer_emmeans_df
```


# Create Data Frames For List 2 Visualization
```{r create data Frames for list 2 visualization}
## data frame for individual subjects data
Data_No_Repeated_Sub_df <- Data_No_Repeated_df %>% 
  group_by(AgeGroup, Subject, ItemType) %>% 
  summarise(List2Recall = mean(L2_Test_Acc), 
            List1Intrusion = mean(L1_Intrusion))

## lowered and raised data points for later visualization
Data_No_Repeated_Sub_df$List2Recall <- ifelse(Data_No_Repeated_Sub_df$List2Recall == 1, .99,
                                       ifelse(Data_No_Repeated_Sub_df$List2Recall == 0, .01,
                                              Data_No_Repeated_Sub_df$List2Recall))

Data_No_Repeated_Sub_df$List1Intrusion <- ifelse(Data_No_Repeated_Sub_df$List1Intrusion == 1, .99,
                                          ifelse(Data_No_Repeated_Sub_df$List1Intrusion == 0, .01,
                                                 Data_No_Repeated_Sub_df$List1Intrusion))
                                              
## reorder factor levels
Data_No_Repeated_Sub_df$ItemType <- factor(Data_No_Repeated_Sub_df$ItemType, levels = c("AB_CD", "AB_AD", "AB_AD_Test", "AB_AD_Test_FB"))
Data_No_Repeated_Sub_df$AgeGroup <- factor(Data_No_Repeated_Sub_df$AgeGroup, levels = c("Younger", "Older"))

## set x axis position for point plots
Data_No_Repeated_Sub_df$x_pos_pnt <- ifelse(Data_No_Repeated_Sub_df$ItemType == "AB_CD", .95,
                                     ifelse(Data_No_Repeated_Sub_df$ItemType == "AB_AD", 1.95, 
                                     ifelse(Data_No_Repeated_Sub_df$ItemType == "AB_AD_Test", 2.95,        
                                     ifelse(Data_No_Repeated_Sub_df$ItemType == "AB_AD_Test_FB", 3.95, "")))) %>% as.numeric()

## set x axis position for violin plots
Data_No_Repeated_Sub_df$x_pos_vio <- ifelse(Data_No_Repeated_Sub_df$ItemType == "AB_CD", 1.05,
                                     ifelse(Data_No_Repeated_Sub_df$ItemType == "AB_AD", 2.05, 
                                     ifelse(Data_No_Repeated_Sub_df$ItemType == "AB_AD_Test", 3.05,        
                                     ifelse(Data_No_Repeated_Sub_df$ItemType == "AB_AD_Test_FB", 4.05, "")))) %>% as.numeric()

## set x axis position for x position mean plots
Data_No_Repeated_Sub_df$x_pos_mean <- ifelse(Data_No_Repeated_Sub_df$ItemType == "AB_CD", 1.04,
                                      ifelse(Data_No_Repeated_Sub_df$ItemType == "AB_AD", 2.04, 
                                      ifelse(Data_No_Repeated_Sub_df$ItemType == "AB_AD_Test", 3.04,        
                                      ifelse(Data_No_Repeated_Sub_df$ItemType == "AB_AD_Test_FB", 4.04, "")))) %>% as.numeric()

## set x axis position for x position mean plots
L2_Recall_glmer_emmeans_df$x_pos_mean <- ifelse(L2_Recall_glmer_emmeans_df$ItemType == "AB_CD", 1.1,
                                         ifelse(L2_Recall_glmer_emmeans_df$ItemType == "AB_AD", 2.1, 
                                         ifelse(L2_Recall_glmer_emmeans_df$ItemType == "AB_AD_Test", 3.1,        
                                         ifelse(L2_Recall_glmer_emmeans_df$ItemType == "AB_AD_Test_FB", 4.1, "")))) %>% as.numeric()

```


# Plot Individual Subject Data For Overall Correct Recall
```{r plot individual subject data for overall correct recall, fig.height=4, fig.width=8}
correct_sub_p <- ggplot(Data_No_Repeated_Sub_df, aes(x = ItemType, y = List2Recall, fill = ItemType)) +
  geom_violinhalf(aes(x = x_pos_pnt), scale = "count") +
  geom_dotplot(aes(fill = ItemType, x = x_pos_pnt), method = "dotdensity", binaxis = "y", stackdir = "down", dotsize = .5, stackratio = .8) +
  stat_summary(aes(x = x_pos_mean), geom = "errorbar", fun.data = "mean_cl_boot", width = 0, size = 1) +
  stat_summary(aes(x = x_pos_mean), geom = "point", fun.y = "mean", shape = 21, size = 3, fill = "black") +
  geom_segment(data = L2_Recall_glmer_emmeans_df, 
               aes(x = x_pos_mean, xend = x_pos_mean, y = asymp.LCL, yend = asymp.UCL),  color = "black", size = 1) + 
  geom_point(data = L2_Recall_glmer_emmeans_df, 
             aes(x = x_pos_mean, y = prob), shape = 23, size = 3,  color = "black", fill = "white") +
  facet_grid(. ~ AgeGroup) +
  scale_fill_manual (values = c("gray100","gray80", "gray60", "gray40")) +
  scale_x_continuous(breaks=seq(1, 4, 1), limits = c(0.5, 4.5), labels = c("A-B, C-D", "A-B, A-D", "A-B, A-D\nTested", "A-B, A-D\nTested\nFeedback")) +
  scale_y_continuous(expand = c(0, 0), limits = c(-0.05, 1.1), breaks = seq(0, 1, .1)) +
  labs(x = "Item Type", y = "List 2 Recall") +
  theme(legend.position = "none",
        legend.key.size = unit(.65, "cm"),
        legend.key=element_rect(color = "black", size = .1),     
        legend.title=element_blank(),
        legend.text=element_blank(),
        strip.background=element_blank(),
        strip.text.x=element_text(size = 16, color = "black", margin = margin(0, 0, 8, 0)),
        strip.text.y=element_blank(),
        axis.ticks.x=element_blank(),
        axis.ticks.y=element_line(size=.3,color="black"),
        axis.text.x=element_text(size=12,color="black"),
        axis.text.y=element_text(size=11,color="black"),
        axis.title.x=element_text(size=16, margin = margin(8, 0, 0, 0), hjust = .5),
        axis.title.y=element_text(size=16, margin = margin(0, 8, 0, 0)),
        plot.margin = unit(c(.15, .15, .15, .15), "in"),
        plot.title = element_text(size = 18, color = "black", hjust = 0, vjust = 3), 
        panel.background = element_blank(),
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
        panel.spacing = unit(-0.01, "cm"),
        panel.border = element_rect(size = .5, fill = NA, color = "black"))
correct_sub_p

ggsave("correct_sub_p.png", plot = correct_sub_p, width = 8, height = 4, units = "in", dpi = 320)

```


# Fit Mixed Effects Model to List 1 Intrusions and Extract Estimated Probabilities
```{r fit mixed effects model to list 1 intrusions and extract estimated probabilities}
## fit model to list 1 intrusions
L1_Intru_glmer <- glmer(L1_Intrusion ~ AgeGroup * ItemType + 
                          (1 | Subject) + (1 | Cue),  
                        family = binomial, 
                        data = Data_No_Repeated_df)

## summary for list 1 intrusions
summary(L1_Intru_glmer)

## anova for list 1 intrusions
Anova(L1_Intru_glmer)

## pairwise comparisons
L1_Intru_glmer_emmeans <- emmeans(L1_Intru_glmer, 
                                   list(pairwise ~ AgeGroup,
                                        pairwise ~ ItemType,
                                        pairwise ~ ItemType | AgeGroup), type = "response")
L1_Intru_glmer_emmeans

## extract estimated probabilities
L1_Intru_glmer_emmeans_df <- as_tibble(L1_Intru_glmer_emmeans$`emmeans of ItemType | AgeGroup`)
L1_Intru_glmer_emmeans_df

## drop control items for visualization
L1_Intru_glmer_emmeans_df %<>% filter(ItemType != "AB_CD") 
L1_Intru_glmer_emmeans_df
```


# Alterations For List 1 Intrusions Visualization
```{r alterations for list 1 intrusions visualization}
## data frame for only changed item types 
Data_AB_AD_Only_Sub_df <- Data_No_Repeated_Sub_df %>%filter(ItemType != "AB_CD")
Data_AB_AD_Only_Sub_df

## set x axis position for x position mean plots
L1_Intru_glmer_emmeans_df$x_pos_mean <- ifelse(L1_Intru_glmer_emmeans_df$ItemType == "AB_AD", 1.1, 
                                        ifelse(L1_Intru_glmer_emmeans_df$ItemType == "AB_AD_Test", 2.1,        
                                        ifelse(L1_Intru_glmer_emmeans_df$ItemType == "AB_AD_Test_FB", 3.1, ""))) %>% as.numeric()

## set x axis position for point plots
Data_AB_AD_Only_Sub_df$x_pos_pnt <- ifelse(Data_AB_AD_Only_Sub_df$ItemType == "AB_AD", .95,
                                    ifelse(Data_AB_AD_Only_Sub_df$ItemType == "AB_AD_Test", 1.95, 
                                    ifelse(Data_AB_AD_Only_Sub_df$ItemType == "AB_AD_Test_FB", 2.95, ""))) %>% as.numeric()

## set x axis position for violin plots
Data_AB_AD_Only_Sub_df$x_pos_vio <- ifelse(Data_AB_AD_Only_Sub_df$ItemType == "AB_AD", 1.05,
                                    ifelse(Data_AB_AD_Only_Sub_df$ItemType == "AB_AD_Test", 2.05, 
                                    ifelse(Data_AB_AD_Only_Sub_df$ItemType == "AB_AD_Test_FB", 3.05, ""))) %>% as.numeric()

## set x axis position for x position mean plots
Data_AB_AD_Only_Sub_df$x_pos_mean <- ifelse(Data_AB_AD_Only_Sub_df$ItemType == "AB_AD", 1.04,
                                     ifelse(Data_AB_AD_Only_Sub_df$ItemType == "AB_AD_Test", 2.04, 
                                     ifelse(Data_AB_AD_Only_Sub_df$ItemType == "AB_AD_Test_FB", 3.04, ""))) %>% as.numeric()
```


# Plot Individual Subject Data For Overall List 1 Intrusions 
```{r plot individual subject data for overall list 1 intrusions, fig.height=4, fig.width=8}
intrusions_sub_p <- ggplot(Data_AB_AD_Only_Sub_df, aes(x = ItemType, y = List1Intrusion, fill = ItemType)) +
  geom_violinhalf(aes(x = x_pos_pnt), scale = "count") +
  geom_dotplot(aes(fill = ItemType, x = x_pos_pnt), method = "dotdensity", binaxis = "y", stackdir = "down", dotsize = .5, stackratio = .8) +
  stat_summary(aes(x = x_pos_mean), geom = "errorbar", fun.data = "mean_cl_boot", width = 0, size = 1) +
  stat_summary(aes(x = x_pos_mean), geom = "point", fun.y = "mean", shape = 21, size = 3, fill = "black") +
  geom_segment(data = L1_Intru_glmer_emmeans_df, 
               aes(x = x_pos_mean, xend = x_pos_mean, y = asymp.LCL, yend = asymp.UCL),  color = "black", size = 1) + 
  geom_point(data = L1_Intru_glmer_emmeans_df, 
             aes(x = x_pos_mean, y = prob), shape = 23, size = 3,  color = "black", fill = "white") +
  facet_grid(. ~ AgeGroup) +
  scale_fill_manual (values = c("gray80", "gray60", "gray40")) +
  scale_x_continuous(breaks=seq(1, 3, 1), limits = c(0.5, 3.5), labels = c("A-B, A-D", "A-B, A-D\nTested", "A-B, A-D\nTested\nFeedback")) +
  scale_y_continuous(expand = c(0, 0), limits = c(-0.05, 1), breaks = seq(0, 1, .1)) +
  labs(x = "Item Type", y = "List 1 Intrusions") +
  theme(legend.position = "none",
        legend.key.size = unit(.65, "cm"),
        legend.key=element_rect(color = "black", size = .1),     
        legend.title=element_blank(),
        legend.text=element_blank(),
        strip.background=element_blank(),
        strip.text.x=element_text(size = 16, color = "black", margin = margin(0, 0, 8, 0)),
        strip.text.y=element_blank(),
        axis.ticks.x=element_blank(),
        axis.ticks.y=element_line(size=.3,color="black"),
        axis.text.x=element_text(size=12,color="black"),
        axis.text.y=element_text(size=11,color="black"),
        axis.title.x=element_text(size=16, margin = margin(8, 0, 0, 0), hjust = .5),
        axis.title.y=element_text(size=16, margin = margin(0, 8, 0, 0)),
        plot.margin = unit(c(.15, .15, .15, .15), "in"),
        plot.title = element_text(size = 18, color = "black", hjust = 0, vjust = 3), 
        panel.background = element_blank(),
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
        panel.spacing = unit(-0.01, "cm"),
        panel.border = element_rect(size = .5, fill = NA, color = "black"))
intrusions_sub_p

ggsave("intrusions_sub_p.png", plot = intrusions_sub_p, width = 8, height = 4, units = "in", dpi = 320)
```


# Change Classifications Probabilities on the Final Cued Recall Test
```{r change classifications probabilities on the final cued recall test}
## summarize change classification responses
Change_Class_prop <- Test_Data_df %>% 
  group_by(AgeGroup, ItemType) %>%
  filter(ItemType %in% c("AB_AD", "AB_AD_Test", "AB_AD_Test_FB")) %>% 
  count(Change_Class) %>% 
  mutate(prop = n / sum(n)) %>%
  select(-n) %>%
  pivot_wider(names_from = Change_Class, values_from = prop) %>%
  select(AgeGroup, ItemType, "Change Recollected", "Change Remembered (Not Recollected)", "Change Not Remembered") %>%
  arrange(desc(AgeGroup)) 
  

Change_Class_prop$Total <- rowSums(Change_Class_prop[, 3:5])
Change_Class_prop

```


# Forward Difference Coding
```{r forward fifference coding}
## re-ordering factor levels for forward difference contrasts
Data_Only_Changed_df$ItemType <- factor(Data_Only_Changed_df$ItemType, levels = c("AB_AD", "AB_AD_Test", "AB_AD_Test_FB"))
Data_Only_Changed_df$AgeGroup <- factor(Data_Only_Changed_df$AgeGroup, levels = c("Younger", "Older"))

## forward difference for factor variable with 2 Age levels
## using "contr.sum" to add to make levels sum to 0
## renaming the columns to clarify the contrasts
contrasts(Data_Only_Changed_df$AgeGroup) <-"contr.sum"
colnames(contrasts(Data_Only_Changed_df$AgeGroup)) <- "Younger_vs_Older"
contrasts(Data_Only_Changed_df$AgeGroup)

## forward difference for factor variable with 4 Item Type levels
## making control items the reference
Data_Only_Changed_df$ItemType <- relevel(Data_Only_Changed_df$ItemType, ref="AB_AD")

## stating the contrasts
contrasts(Data_Only_Changed_df$ItemType)[,1] <- c(2/3,-1/3,-1/3)
contrasts(Data_Only_Changed_df$ItemType)[,2] <- c(1/3,1/3,-2/3)

## renaming the columns to clarify the contrasts
colnames(contrasts(Data_Only_Changed_df$ItemType)) <- c("AB_AD_vs_AB_AD_Test", 
                                                    "AB_AD_Test_vs_AB_AD_Test_FB")
```


# Fit Mixed Effects Model to Change Recollection and Extract Estimated Probabilities
```{r fit Mixed Effects Model to Change Recollection and Extract Estimated Probabilities}
## fit model to change recollection
Change_Recollection_glmer <- glmer(ChangeRecollected ~ AgeGroup * ItemType + 
                                     (1 | Subject) + (1 | Cue), 
                                   family = binomial,
                                   data = Data_Only_Changed_df)

## anova to change recollection
Anova(Change_Recollection_glmer)

## summary to change recollection
summary(Change_Recollection_glmer)

## pairwise comparisons
Change_Recollection_glmer_emmeans <- emmeans(Change_Recollection_glmer, 
                                            list(pairwise ~ ItemType,
                                                 pairwise ~ AgeGroup,
                                                 pairwise ~ ItemType | AgeGroup), type = "response")
Change_Recollection_glmer_emmeans

## extract estimated probabilities
Change_Recollection_glmer_emmeans_df <- as_tibble(Change_Recollection_glmer_emmeans$`emmeans of ItemType | AgeGroup`)
Change_Recollection_glmer_emmeans_df
```


# Forward Difference Coding For Recall Conditionalized on Change Classifications
```{r forward difference coding for recall conditionalized on change classifications}
# making Recollected the reference
Data_Only_Changed_df$ChangeRecollected_Fig <- relevel(Data_Only_Changed_df$ChangeRecollected_Fig, ref="Recollected")

# using "contr.sum" to add to make levels sum to 0
contrasts(Data_Only_Changed_df$ChangeRecollected_Fig)<-"contr.sum"
colnames(contrasts(Data_Only_Changed_df$ChangeRecollected_Fig)) <- "Recollected_vs_NotRecollected"
contrasts(Data_Only_Changed_df$ChangeRecollected_Fig)
```


# Fit Mixed Effects Model to List 2 Recall Conditionalized on Change Classifications
```{r fit mixed effects model to list 2 recall conditionalized on change classifications}
## fit model to list 2 recall accuracy conditionalized on change classification
L2_Recall_Cond_glmer <- glmer(L2_Test_Acc ~ AgeGroup * ItemType * ChangeRecollected_Fig +
                              (1 | Subject) + (1 | Cue), 
                              family = binomial, 
                              control = more_control, 
                              data = Data_Only_Changed_df)

## Anova for List 2 recall accuracy conditionalized on change classification
Anova(L2_Recall_Cond_glmer)

## Summary for List 2 recall accuracy conditionalized on change classification
summary(L2_Recall_Cond_glmer)

## pairwise comparisons
L2_Recall_Cond_glmer_emmeans <- emmeans(L2_Recall_Cond_glmer, 
                                        list(pairwise ~ AgeGroup | ChangeRecollected_Fig,
                                             pairwise ~ ItemType | AgeGroup | ChangeRecollected_Fig), type = "response")
L2_Recall_Cond_glmer_emmeans

## extract estimated probabilities
L2_Recall_Cond_glmer_emmeans_df <- as_tibble(L2_Recall_Cond_glmer_emmeans$emmeans)
L2_Recall_Cond_glmer_emmeans_df
```


# Combine Data Frames for Change Class
```{r combine data frames for change class}
## summarize change classification responses
Change_Recollected_prop <- Data_Only_Changed_df %>% 
  group_by(AgeGroup, ItemType) %>%
  filter(ItemType %in% c("AB_AD", "AB_AD_Test", "AB_AD_Test_FB")) %>% 
  count(ChangeRecollected_Fig) %>% 
  mutate(prop = n / sum(n)) %>%
  select(-n) %>%
  pivot_wider(names_from = ChangeRecollected_Fig, values_from = prop) %>% 
  select(AgeGroup, ItemType, "Recollected", "Not Recollected") %>%
  arrange(desc(AgeGroup))
Change_Recollected_prop$Total <- rowSums(Change_Recollected_prop[, 3:4])
Change_Recollected_prop

## convert data frame to long format
Change_Recollected_prop_l <- Change_Recollected_prop %>% 
  select(-Total) %>%
  pivot_longer(cols = c("Recollected", "Not Recollected"), 
                 names_to = "ChangeRecollected_Fig", values_to = "changeprob")
Change_Recollected_prop_l

## data frame for conditionalized means
List2_Recall_Cond_obs_Mean <- Data_Only_Changed_df %>% 
  group_by(AgeGroup, ItemType, ChangeRecollected_Fig) %>%
  filter(ItemType %in% c("AB_AD", "AB_AD_Test", "AB_AD_Test_FB")) %>% 
  summarise(L2_Recall = mean(L2_Test_Acc))
List2_Recall_Cond_obs_Mean
  
# join change recollection and list 2 recollection data frames
List2_Recall_Cond <- L2_Recall_Cond_glmer_emmeans_df %>% 
  left_join(Change_Recollected_prop_l) %>% 
  left_join(List2_Recall_Cond_obs_Mean)
List2_Recall_Cond

## data frame for subjects
List2_Recall_Cond_sub <- Data_Only_Changed_df %>% 
  group_by(Subject, AgeGroup, ItemType, ChangeRecollected_Fig) %>%
  filter(ItemType %in% c("AB_AD", "AB_AD_Test", "AB_AD_Test_FB")) %>% 
  summarise(L2_Recall = mean(L2_Test_Acc)) %>% 
  left_join(Change_Recollected_prop_l)
List2_Recall_Cond_sub
```


# Alterations For List 2 Recall Conditionalized
```{r alterations for list 2 recall conditionalized}
## re-order factor levels
List2_Recall_Cond$ChangeRecollected_Fig <- factor(List2_Recall_Cond$ChangeRecollected_Fig, levels = c("Recollected", "Not Recollected"))
List2_Recall_Cond_sub$ChangeRecollected_Fig <- factor(List2_Recall_Cond_sub$ChangeRecollected_Fig, levels = c("Recollected", "Not Recollected"))

## set x axis position for x position mean plots
List2_Recall_Cond$x_pos_mean <- ifelse(List2_Recall_Cond$ItemType == "AB_AD", 1.1, 
                                ifelse(List2_Recall_Cond$ItemType == "AB_AD_Test", 2.1,        
                                ifelse(List2_Recall_Cond$ItemType == "AB_AD_Test_FB", 3.1, ""))) %>% as.numeric()

## set x axis position for point plots
List2_Recall_Cond_sub$x_pos_pnt <- ifelse(List2_Recall_Cond_sub$ItemType == "AB_AD", .95,
                                   ifelse(List2_Recall_Cond_sub$ItemType == "AB_AD_Test", 1.95, 
                                   ifelse(List2_Recall_Cond_sub$ItemType == "AB_AD_Test_FB", 2.95, ""))) %>% as.numeric()

## set x axis position for violin plots
List2_Recall_Cond_sub$x_pos_vio <- ifelse(List2_Recall_Cond_sub$ItemType == "AB_AD", 1.05,
                                   ifelse(List2_Recall_Cond_sub$ItemType == "AB_AD_Test", 2.05, 
                                   ifelse(List2_Recall_Cond_sub$ItemType == "AB_AD_Test_FB", 3.05, ""))) %>% as.numeric()

## set x axis position for x position mean plots
List2_Recall_Cond_sub$x_pos_mean <- ifelse(List2_Recall_Cond_sub$ItemType == "AB_AD", 1.03,
                                    ifelse(List2_Recall_Cond_sub$ItemType == "AB_AD_Test", 2.03, 
                                    ifelse(List2_Recall_Cond_sub$ItemType == "AB_AD_Test_FB", 3.03, ""))) %>% as.numeric()
```


# Plot Individual Subject Data For List 2 Recall Conditionalized
```{r plot individual subject data for list 2 recall conditionalized, fig.height=6, fig.width=14}
list2_recall_con_sub_p <- ggplot(List2_Recall_Cond_sub, aes(x = ItemType, y = L2_Recall, fill = interaction(ItemType, ChangeRecollected_Fig))) +
  geom_violinhalf(aes(x = x_pos_pnt, fill = ItemType), scale = "count") +
  geom_dotplot(aes(fill = ItemType, x = x_pos_pnt), method = "dotdensity", binaxis = "y", stackdir = "down", dotsize = .5, stackratio = .8) +
  stat_summary(aes(x = x_pos_mean), geom = "errorbar", color = "black", fun.data = "mean_cl_boot", width = 0, size = 1) +
  stat_summary(aes(x = x_pos_mean, size = changeprob), geom = "point", fun = "mean", shape = 21, color = "black") +
  geom_segment(data = List2_Recall_Cond, 
               aes(x = x_pos_mean, xend = x_pos_mean, y = asymp.LCL, yend = asymp.UCL), color = "black", size = 1) + 
  geom_point(data = List2_Recall_Cond, 
             aes(x = x_pos_mean, y = prob, size = changeprob), shape = 23, color = "black", fill = "white") +
  facet_grid(ChangeRecollected_Fig ~ AgeGroup) +
  scale_fill_manual(values = c("gray85", "gray60", "gray45", "firebrick2", "forestgreen", "firebrick2", "forestgreen", "firebrick2", "forestgreen")) +
  scale_size_continuous(range = c(4.5, 8)) +
  scale_x_continuous(breaks=seq(1, 3, 1), limits = c(0.5, 3.5), labels = c("A-B, A-D", "A-B, A-D\nTested", "A-B, A-D\nTested\nFeedback")) +
  scale_y_continuous(expand = c(0, 0), limits = c(-0.05, 1.05), breaks = seq(0, 1, .1)) +
  labs(x = "Item Type", y = "List 2 Recall Conditionalized") +
  theme(legend.position = "none",
        legend.key.size = unit(.65, "cm"),
        legend.key=element_rect(color = "black", size = .1),     
        legend.title=element_blank(),
        legend.text=element_text(size = 12),
        strip.background=element_blank(),
        strip.text.x=element_text(size = 18, color = "black", margin = margin(0, 0, 8, 0)),
        strip.text.y=element_text(size = 18, color = "black", margin = margin(0, 0, 0, 8)),
        axis.ticks.x=element_blank(),
        axis.ticks.y=element_line(size=.3,color="black"),
        axis.text.x=element_text(size=14,color="black"),
        axis.text.y=element_text(size=13,color="black"),
        axis.title.x=element_text(size=18, margin = margin(8, 0, 0, 0), hjust = .5),
        axis.title.y=element_text(size=18, margin = margin(0, 8, 0, 0)),
        plot.margin = unit(c(.15, .15, .15, .15), "in"),
        panel.background = element_blank(),
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
        panel.spacing = unit(-0.01, "cm"),
        panel.border = element_rect(size = .5, fill = NA, color = "black"))
list2_recall_con_sub_p
```


# Fit Mixed Effects Model to List 1 Intrusions Conditionalized and Extract Estimated Probabilities
```{r fit mixed effects model to list 1 intrusions conditionalized and extract estimated probabilities}
# fit model to list 1 intrusions
L1_Intru_Cond_glmer <- glmer(L1_Intrusion ~ AgeGroup * ItemType * ChangeRecollected_Fig 
                             + (1 | Subject) + (1 | Cue), 
                             family = binomial, 
                             control = more_control, 
                             data = Data_Only_Changed_df)

# Anova for list 1 intrusions
Anova(L1_Intru_Cond_glmer)

# Summary for list 1 intrusions
summary(L1_Intru_Cond_glmer)

## pairwise comparisons
L1_Intru_Cond_glmer_emmeans <- emmeans(L1_Intru_Cond_glmer, 
                                pairwise ~ ItemType | AgeGroup | ChangeRecollected_Fig, type = "response")
L1_Intru_Cond_glmer_emmeans

## extract estimated probabilities
L1_Intru_Cond_glmer_emmeans_df <- as_tibble(L1_Intru_Cond_glmer_emmeans$emmeans)
L1_Intru_Cond_glmer_emmeans_df %<>% select(-df) %>% mutate_if(is.numeric, round, digits = 3)
L1_Intru_Cond_glmer_emmeans_df
```


# Fit Mixed Effects Model to List 1 Intrusions Conditionalized on Change Not Recollected and Extract Estimated Probabilities
```{r fit mixed effects model to list 1 intrusions conditionalized on change not recollected and extract estimated probabilities}
## fit model to list 1 intrusions
L1_Intru_Cond_NoCR_glmer <- glmer(L1_Intrusion ~ AgeGroup * ItemType * Change_Class +
                             (1 | Subject) + (1 | Cue), 
                             family = binomial, 
                             control = more_control, 
                             data = Data_Only_Changed_df, subset = Change_Class != "Change Recollected")

# Anova for list 1 intrusions
Anova(L1_Intru_Cond_NoCR_glmer)

## pairwise comparisons
L1_Intru_Cond_NoCR_glmer_emmeans <- emmeans(L1_Intru_Cond_NoCR_glmer, 
                                pairwise ~ ItemType | AgeGroup | Change_Class, type = "response")
L1_Intru_Cond_NoCR_glmer_emmeans

## extract estimated probabilities
L1_Intru_Cond_NoCR_glmer_emmeans_df <- as_tibble(L1_Intru_Cond_NoCR_glmer_emmeans$emmeans)
L1_Intru_Cond_NoCR_glmer_emmeans_df %<>% select(-df) %>% mutate_if(is.numeric, round, digits = 3)
L1_Intru_Cond_NoCR_glmer_emmeans_df
```


# Combine data frames
```{r combine data frames}
## summarize no change recollection responses
No_Change_Recollection_prop <- Data_Only_Changed_df %>% 
  group_by(AgeGroup, ItemType) %>%
  filter(ItemType %in% c("AB_AD", "AB_AD_Test", "AB_AD_Test_FB")) %>% 
  # filter(Change_Class %in% c("Change Not Remembered", "Change Remembered (Not Recollected)")) %>% 
  count(Change_Class) %>% 
  mutate(prop = n / sum(n)) %>%
  select(-n) %>%
  pivot_wider(names_from = Change_Class, values_from = prop) %>% 
  select(AgeGroup, ItemType, "Change Not Remembered", "Change Remembered (Not Recollected)") %>%
  arrange(desc(AgeGroup))

No_Change_Recollection_prop$Total <- rowSums(No_Change_Recollection_prop[, 3:4])
No_Change_Recollection_prop

## convert data frame to long format
No_Change_Recollection_prop_l <- No_Change_Recollection_prop %>% 
  select(-Total) %>%
  pivot_longer(cols = c("Change Not Remembered", "Change Remembered (Not Recollected)"), 
                 names_to = "Change_Class", values_to = "classprob")
No_Change_Recollection_prop_l

## data frame for conditionalized means
List1_Intru_Cond_obs_Mean <- Data_Only_Changed_df %>% 
  group_by(AgeGroup, ItemType, Change_Class) %>%
  filter(ItemType %in% c("AB_AD", "AB_AD_Test", "AB_AD_Test_FB")) %>%
  filter(Change_Class %in% c("Change Not Remembered", "Change Remembered (Not Recollected)")) %>% 
  summarise(L1_Intru = mean(L1_Intrusion))
List1_Intru_Cond_obs_Mean
  
# join change recollection and list 1 intrusions data frames
List1_Intru_Cond <- L1_Intru_Cond_NoCR_glmer_emmeans_df %>% 
  left_join(No_Change_Recollection_prop_l) %>% 
  left_join(List1_Intru_Cond_obs_Mean)
List1_Intru_Cond

## data frame for subjects
List1_Intru_Cond_sub <- Data_Only_Changed_df %>% 
  group_by(Subject, AgeGroup, ItemType, Change_Class) %>%
  filter(ItemType %in% c("AB_AD", "AB_AD_Test", "AB_AD_Test_FB")) %>%
  filter(Change_Class %in% c("Change Not Remembered", "Change Remembered (Not Recollected)")) %>% 
  summarise(L1_Intru = mean(L1_Intrusion)) %>% 
  left_join(No_Change_Recollection_prop_l)
List1_Intru_Cond_sub
```


# Alterations For List 1 Intrusions Conditionalized
```{r alterations for list 1 Intrusions conditionalized}
## re-order factor levels
List1_Intru_Cond$Change_Class <- factor(List1_Intru_Cond$Change_Class, 
                                        levels = c("Change Remembered (Not Recollected)", "Change Not Remembered"))
List1_Intru_Cond_sub$Change_Class <- factor(List1_Intru_Cond_sub$Change_Class, 
                                        levels = c("Change Remembered (Not Recollected)", "Change Not Remembered"))

## set x axis position for x position mean plots
List1_Intru_Cond$x_pos_mean <- ifelse(List1_Intru_Cond$ItemType == "AB_AD", 1.1, 
                                ifelse(List1_Intru_Cond$ItemType == "AB_AD_Test", 2.1,        
                                ifelse(List1_Intru_Cond$ItemType == "AB_AD_Test_FB", 3.1, ""))) %>% as.numeric()

## set x axis position for point plots
List1_Intru_Cond_sub$x_pos_pnt <- ifelse(List1_Intru_Cond_sub$ItemType == "AB_AD", .95,
                                   ifelse(List1_Intru_Cond_sub$ItemType == "AB_AD_Test", 1.95, 
                                   ifelse(List1_Intru_Cond_sub$ItemType == "AB_AD_Test_FB", 2.95, ""))) %>% as.numeric()

## set x axis position for violin plots
List1_Intru_Cond_sub$x_pos_vio <- ifelse(List1_Intru_Cond_sub$ItemType == "AB_AD", 1.05,
                                   ifelse(List1_Intru_Cond_sub$ItemType == "AB_AD_Test", 2.05, 
                                   ifelse(List1_Intru_Cond_sub$ItemType == "AB_AD_Test_FB", 3.05, ""))) %>% as.numeric()

## set x axis position for x position mean plots
List1_Intru_Cond_sub$x_pos_mean <- ifelse(List1_Intru_Cond_sub$ItemType == "AB_AD", 1.03,
                                    ifelse(List1_Intru_Cond_sub$ItemType == "AB_AD_Test", 2.03, 
                                    ifelse(List1_Intru_Cond_sub$ItemType == "AB_AD_Test_FB", 3.03, ""))) %>% as.numeric()
```


# Plot Individual Subject Data For List 1 Intrusions Conditionalized
```{r plot individual subject data for list 1 intrusions conditionalized, fig.height=6, fig.width=14}
list1_intru_con_sub_p <- ggplot(List1_Intru_Cond_sub, aes(x = ItemType, y = L1_Intru, fill = interaction(ItemType, Change_Class))) +
  geom_violinhalf(aes(x = x_pos_pnt, fill = ItemType), scale = "count") +
  geom_dotplot(aes(fill = ItemType, x = x_pos_pnt), method = "dotdensity", binaxis = "y", stackdir = "down", dotsize = .5, stackratio = .8) +
  stat_summary(aes(x = x_pos_mean), geom = "errorbar", color = "black", fun.data = "mean_cl_boot", width = 0, size = 1) +
  stat_summary(aes(x = x_pos_mean, size = classprob), geom = "point", fun = "mean", shape = 21, color = "black") +
  geom_segment(data = List1_Intru_Cond, 
               aes(x = x_pos_mean, xend = x_pos_mean, y = asymp.LCL, yend = asymp.UCL), color = "black", size = 1) + 
  geom_point(data = List1_Intru_Cond, 
             aes(x = x_pos_mean, y = prob, size = classprob), shape = 23, color = "black", fill = "white") +
  facet_grid(Change_Class ~ AgeGroup) +
  scale_fill_manual(values = c("gray80", "gray60", "gray40", "firebrick2", "blue2", "firebrick2", "blue2", "firebrick2", "blue2")) +
  scale_size_continuous(range = c(4.5, 8)) +
  scale_x_continuous(breaks=seq(1, 3, 1), limits = c(0.5, 3.5), labels = c("A-B, A-D", "A-B, A-D\nTested", "A-B, A-D\nTested\nFeedback")) +
  scale_y_continuous(expand = c(0, 0), limits = c(-0.05, 1.05), breaks = seq(0, 1, .1)) +
  labs(x = "Item Type", y = "List 1 Intrusions Conditionalized") +
  theme(legend.position = "none",
        legend.key.size = unit(.65, "cm"),
        legend.key=element_rect(color = "black", size = .1),     
        legend.title=element_blank(),
        legend.text=element_text(size = 12),
        strip.background=element_blank(),
        strip.text.x=element_text(size = 18, color = "black", margin = margin(0, 0, 8, 0)),
        strip.text.y=element_text(size = 18, color = "black", margin = margin(0, 0, 0, 8)),
        axis.ticks.x=element_blank(),
        axis.ticks.y=element_line(size=.3,color="black"),
        axis.text.x=element_text(size=14,color="black"),
        axis.text.y=element_text(size=13,color="black"),
        axis.title.x=element_text(size=18, margin = margin(8, 0, 0, 0), hjust = .5),
        axis.title.y=element_text(size=18, margin = margin(0, 8, 0, 0)),
        plot.margin = unit(c(.15, .15, .15, .15), "in"),
        panel.background = element_blank(),
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
        panel.spacing = unit(-0.01, "cm"),
        panel.border = element_rect(size = .5, fill = NA, color = "black"))
list1_intru_con_sub_p
```


